Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2017-03-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
a little more cp 8

\subsubsection{Grid Size Analysis}
Figure~\ref{FHNG01_RI} shows the comparison of the centerline gas burner temperatures with three different sets of FDS results.  The only variable in the simulations is the RI. The RIs include three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).  The associated 95~\% confidence limits are also shown the temperature value for each height.  The FDS simulated temperatures based on the course cell size of 80~mm (RI=5) has the best agreement with the temperatures along centerline of the plume.  The two simulations with the higher RI values provide less agreement that the course mesh.  This seems to be counter intuitive to the results expected from an increased RI.  However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich) which results in temperatures significantly lower than measured.  This affect of this fuel rich area above the burner results poorer agreement with increasing RI.  It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone is higher than what was measured.

>>>>

\subsubsection{Grid Size Analysis}
Figure~\ref{FHNG01_RI} shows the comparison of the centerline gas burner temperatures with three different sets of FDS results.  The only variable in the simulations is the RI. The RIs include three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).  The associated 95~\% confidence limits are also shown the temperature value for each height.  The FDS simulated temperatures based on the course cell size of 80~mm (RI=5) has the best agreement with the temperatures along centerline of the plume.  The two simulations with the higher RI values provide less agreement that the course mesh.  This seems to be counter intuitive to the results expected from an increased RI.  However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich) which results in temperatures significantly lower than measured.  The affect of this fuel rich area above the burner results in poorer agreement with increasing RI.  It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone is moved to a higher elevation relative to what was measured.  For example the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases respectively, seem to coincide with the measured value at 0.3~m above the burner.  Making the adjustment appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.

These simulation results are consistant with the comparison made to the McCaffery ref   in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
